The pollination trade-off

### 2019-05-07 paper/supp-info.Rmd
Move plot conspecific vs heterospecific pollen to the supplementary

```{r table-open-bagged-models-general, results = "asis"}
drake::loadd(open_bagged_model)

@@

```{r table-open-bagged-models-random, results='asis'}
drake::loadd(con_con_plot_df)

>>>>

```{r fig-conspecififc-heterospecific, fig.height=2, fig.width = 3.57, fig.cap="Despite the variation in these slopes, plants overall had more conspecific than heterospecific pollen deposited in their stigmas."}
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
drake::loadd(fig_hetero_con)
fig_hetero_con
```

```{r table-open-bagged-models-general, results = "asis", eval = FALSE}
drake::loadd(open_bagged_model)

@@

```{r table-open-bagged-models-random, results='asis', eval = FALSE}
drake::loadd(con_con_plot_df)
